As mentioned the project is focusing on a user-centric tool. A list of user stories was created for the client
explaining the way he and any potential user was going to interact with the framework. The list
of stories was later iterated until there were set of user stories defining each of the sprints
as seen in figure \ref{table:userstories}.
\begin{table}[ht] 
\caption{Sprint one and sprint two of the framework} % title of Table 
\centering % used for centering table 
\begin{tabular}{l} % centered columns (4 columns) 
\hline\hline %inserts double horizontal lines 
Sprint One\\ [0.5ex] % inserts table 
%heading 
\hline % inserts single horizontal line
User should be able to disable/enable logging\\
User should set up only one configuration file\\
Users should be able to see individuals in infix notation\\
Users should be able to set arguments only through the fitness function \\

\hline\hline 
Sprint Two\\
\hline
User must be able to set target service to copy\\
User should be able to graph individuals\\
User should configure the framework through XML\\
\hline\hline 
Sprint Three\\
\hline
Users should chose from pre-set primitive functions\\
User should be able to generate XML file through a GUI\\
User should modify the incoming result from http response\\
User should modify the outgoing http request \\
\hline\hline 
\end{tabular} 
\label{table:userstories} % is used to refer this table in the text 
\end{table}

\begin{enumerate}
\item \textbf{Sprint One} was focused on evaluating individuals remotely
	\begin{enumerate}
	\item Configuration of basic genetic programming parameters.
	\item Create a class for defining and reading of primitive set.
	\item Converting DEAP individual to python code for easier evaluation.
	\item Create a base for cloning webservices.
	\end{enumerate}
\item \textbf{Sprint Two} was focused on cloning a web service.
	\begin{enumerate}
	\item Use existing web service as a fitness function.
	\item Automation of configuration.
	\item Use a single URL for selecting the target webservice.
	\end{enumerate}
\item \textbf{Sprint Three} aimed for creating a more interactive and easy way to configure the system.
	\begin{enumerate}
	\item Use of XML file to configure the framework.
	\item Create GUI for generating the XML file.
	\item Providing request and response handlers for handling communication with webservices.
	\end{enumerate}
\end{enumerate}
