DEAP stands for distributed evolutionary algorithms in python. It is a framework that supports both genetic algorithms and genetic programming.
It seeks to make algorithms explicit and data structures transparent. Hence making genetic programming easy by providing easy way for primitives
to be created and access to pre set crossover and mutation algorithms. Each of its features can be fine tuned through multiple parameters so it's not creating
heavy constraints.
\paragraph{}
As similar to Darwin, DEAP is emphasizing on loose coupling in its design, it uses multiple components that provide the necessary functionality
for the framework. The \textit{pset} is a class through which all the configuration related to the primitive set is done. Primitives are defined
through mapping any defined function or method and declaring the amount of arguments they are taking. In addition the terminals are defined where
there is a pre-set of constants that can be utilized. Arguments for the genetic program are also defined in through the \textit{pset} hence 
separating it from other components so it can be extracted and manipulated individually.
\paragraph{}
Another core component of the DEAP framework is the \textit{toolbox}. This is the component where the genetic programming is configured. Parameters
like maximum depth of an individuals are specified, the algorithms for crossover and mutation. The framework gives the flexibility to define your
own mutation and crossover algorithms as well as manipulate their rates and the size of the population and generation. Fitness function is specified in the toolbox 
and later maps to the toolbox. After all the configuration of the primitive set and the genetic
programming parameters is done the population is generated. There is an automatic way of doing it through special DEAP functions however for Darwin
a more complex approach was chosen which will be later explained. In the end there is the statistics module that takes the generations and creates
set of statistics that can be displayed ( e.g. mean of a generation, best and worst individual ).

