By separating the framework into several base components it was easier to split each of the components into
its core functions and apply unit tests to verify their correctness. However due to the complexity and
dependencies in the framework, test writing was complicated. Many of the functions depended either on 
the DEAP toolbox or on the primitive set which was responsible for generating DEAP individuals. They couldn't
be reproduced manually for the tests, so multiple components had to be enabled in order to verify the unit tests.
Since DEAP was an external framework with a stable release it was assumed that it is functioning correctly so no 
unit tests were ran on it specifically however components using it were extensively tested. Each of the components
had testing aims however not all functions were covered since their complexity or dependency was too high, thats why
they were left for system testing later on. This was the unit testing strategy:

\begin{enumerate}
  \item Unit tests on each of PrimitiveConfig's methods
  \begin{enumerate}
	\item Test pre-set primitives
	\item Test code generation
	\item Test utility functions
  \end{enumerate}  
  \item Test all of Populator's methods without the configuration methods or the more complicated ones which would be part of the system testing.
  \begin{enumerate}
	\item Test methods related to individual manipulation
	\item Test code generation
	\item Test fitness gathering functions 
  \end{enumerate}  
  \item Handle all the functions in the helper module excluding Proxy class that is going to be aprt of the system testing.
  \begin{enumerate}
	\item Test utility functions
	\item Test code generation
  \end{enumerate} 
\end{enumerate}

Through the unit tests many errors in the code generation functions were found so they had to be re factored. The imports used for the custom primitive set
weren't working properly so they had to be fixed. After the unit tests were created initially they were used for verification of code correctness after
a change in the code. If the unit test didn't work that meant there was an error in the code.
\paragraph{}
Among the bugs found through unit tests was a code generation one. The python source was missing the imports specified by the user. When a simple system
test was ran it couldn't be identified since the primitives used didn't include any external imports. However because of the modified configuration used
for unit testing the bug was identified on time.
\paragraph{}
Another problem was with the pre-set primitives. Because of the mathematical nature of primitives division by 0 had to be avoided.
In the simple system tests there were no examples with division by 0, the bug wasn't found until unit tests
for each primitive were executed.