Important feature for a framework is usability. Participants were used to evaluate the quality of the framework and check if the goals
to create an easy to use and simple framework were achieved. The participants were presented with tutorial for the framework and it's documentation
each of them had to have basic knowledge in programming. The choice of first to fourth year students presented a good study group since it presented people
from different programming experience. The participants had to asses the quality of the 
tutorial and documentation and answer the following questions:

\begin{enumerate}
\item Was it helpful to understand the basics of the framework?
\item How complex it was to create the first examples? 
\item Were you given enough information to continue working with the framework on your own?
\item Do you feel confident that you understand the framework basics? 
\end{enumerate}
 
In another part of the evaluation they had to asses the graphical user interface. They had to answer the following questions: 

\begin{enumerate}
\item Was it intuitive enough?
\item Was it simple?
\item Was it complex? 
\item Did it present enough options?
\item Did it present too many options?
\item Would you think tips would be helpful above each field?
\item Can you give additional feedback that can help improve the GUI
\end{enumerate}

In addition through the evaluation the participants were observed and note on their actions were taken to compare with their feedback. This way a more
accurate conclusions could be drawn so the correct features could be improved and re-worked.

The studies helped spot problems in...[wait for results] 